% Employment Experience section

\section{\textcolor{airforceblue}{EMPLOYMENT EXPERIENCE}}
  \employmentSubheadingListStart

    \employmentSubheading
      {Lead Sonographer}{} 
  {University Health Network - Toronto, ON, Canada}{2023 - 2025}
      \resumeItemListStart        
            \resumeItem{Led cross-functional teams of sonographers across 3 major institutions (Princess Margaret, Toronto General, and Toronto Western) to ensure optimal staffing for time-sensitive, high-impact initiatives.}
            \resumeItem{Boosted appointment capacity by 12\% by leveraging data analytics and predictive modeling to uncover key operational insights; translated insights into actionable strategies adopted by senior leadership.}
            \resumeItem{Drove a 6\% increase in patient throughput by applying time-series analysis to workflow patterns, identifying bottlenecks, and implementing scalable process improvements across multiple sites.}  
            \resumeItem{Enhanced team engagement and retention by 50\% through development of targeted onboarding and training programs, ensuring organizational continuity and stronger employer brand perception.}  
      \resumeItemListEnd  

    \employmentSubheading
      {Sonographer}{} 
  {University Health Network - Toronto, ON, Canada}{2021 - 2023}
      \resumeItemListStart
            \resumeItem{Boosted client satisfaction scores by 10\% by conducting data-driven analysis of patient feedback and departmental KPIs, aligning workflows across 12+ departments for improved service delivery.}
            \resumeItem{[TODO] Improved client experience by 10\% by synthesizing feedback analytics and KPIs, aligning workflows across 12+ departments to deliver consistent, customer-centric service delivery.}
            \resumeItem{Eliminated 60-minute wait times and increased daily appointment volume by redesigning and optimizing scheduling processes, driving operational efficiency.}  
            \resumeItem{Reduced documentation errors by 25\% through creation of targeted EPIC training programs, leveraging utilization data to address staff needs and enhance compliance.}  
      \resumeItemListEnd

    \employmentSubheading
      {Sonography Intern}{} 
  {Humber River Hospital - Toronto, ON, Canada}{2020 - 2020}
      \resumeItemListStart
            \resumeItem{Implemented compliance-driven training on research protocols, ensuring regulatory alignment and increasing equipment utilization by 30\%.}
            \resumeItem{Played a key role in ISO accreditation, ensuring 100\% compliance thus strengthening the institution’s credibility and market positioning.}
    \resumeItemListEnd

    \employmentSubheading
      {Cell Biology Laboratory Teaching Assistant}{} 
  {University of Waterloo - Waterloo, ON, Canada}{2014 - 2015}
      \resumeItemListStart
            \resumeItem{Designed and managed weekly lab sessions, grading over 250 assessments per term.}
            \resumeItem{Implemented instructional strategies that improved student performance by 15\%.}
    \resumeItemListEnd  
      
  \employmentSubheadingListEnd
\vspace{-12pt}
